---
title: "Lorenzo Fabbri"
cv-tagline: "Postdoctoral Researcher in Epidemiology"
cv-email: "lorenzo.fabbri92sm@gmail.com"
cv-location: "Madrid, Spain"
cv-website: "lorenzofabbri.github.io/epilorenzo"
cv-orcid: "0000-0003-3031-322X"
cv-scholar: "QbPv1H0AAAAJ"
cv-github: "lorenzoFabbri"
cv-linkedin: "lorenzo-fabbri-303185383"
cv-bluesky: "epilorenzo.bsky.social"
---

```{r setup}
#| results: asis
source("R/data.R")
source("R/render.R")
knitr::opts_chunk$set(results = "asis")
```

::: {.content-visible unless-format="typst"}
::: {.cv-header}
*{{< meta cv-tagline >}}*

[{{< meta cv-email >}}](mailto:{{< meta cv-email >}}) | {{< meta cv-location >}} | [{{< meta cv-website >}}](https://{{< meta cv-website >}}) | [ORCID](https://orcid.org/{{< meta cv-orcid >}}) | [Google Scholar](https://scholar.google.com/citations?user={{< meta cv-scholar >}}) | [GitHub](https://github.com/{{< meta cv-github >}}) | [LinkedIn](https://linkedin.com/in/{{< meta cv-linkedin >}}) | [Bluesky](https://bsky.app/profile/{{< meta cv-bluesky >}})
:::
:::

::: {.content-visible when-format="html"}
<div class="cv-download-links">
[Download PDF](index.pdf){.btn} [Download DOCX](index.docx){.btn}
</div>
:::

## Research Interests

Cancer epidemiology, causal inference, and evidence triangulation.

## Academic Appointments

```{r}
render_affiliations(cv_data$employments)
```

## Education

```{r}
edu_details <- list(
  # PG Certificate in Public Health, LSHTM
  "26799263" = "Basic Epidemiology (PHM101)",
  # Graduate Certificate, Open University
  "23612750" = "Mathematical Statistics (M347): 91/100 With Distinction",
  # PhD Programme in Biomedicine, UPF
  "16645010" = paste(
    "Thesis: Early Life Exposure to Environmental Chemicals and",
    "Neurodevelopment through Childhood and Adolescence.",
    "Supervisor: Prof. Martine Vrijheid"
  ),
  # M.Sc. in Quantitative and Computational Biology, Trento
  "9421733" = paste(
    "Thesis (FBK, Trento): Machine Learning for Predictive Drug Induced",
    "Hepatotoxicity. Supervised by: Dr. Cesare Furlanello, Dr. Marco Chierici,",
    "Prof. Enrico Domenici.",
    "Internship (HITS, Heidelberg): Machine and Deep Learning for Predictive",
    "Unbinding Kinetics of Kinases. Supervised by: Prof. Rebecca Wade,",
    "Dr. Daria Kokh, Prof. Raffaello Potestio.",
    "Final mark: 110/110 With Honors"
  ),
  # M.Sc. Student in Computational Science, USI
  "16695943" = paste(
    "Project (USI, Lugano): Investigation by Computational Techniques of",
    "Channelopathies Related to Sodium Channels.",
    "Supervised by: Prof. Vittorio Limongelli, Prof. Daniele Di Marino"
  ),
  # B.Sc. in Biotechnology, Parma
  "16695935" = paste(
    "Thesis (RWTH, Aachen): Whole Body PBPK Modeling of Valproic Acid.",
    "Supervised by: Prof. Elena Maestri, Prof. Lars M. Blank, Dr. Henrik Cordes.",
    "Final mark: 103/110"
  )
)

render_affiliations(cv_data$educations, details = edu_details)
```

## Research Visits

```{r}
render_affiliations(cv_data$invited)
```

## Grants and Fellowships

```{r}
render_fundings(cv_data$fundings)
```

## Honors and Awards

```{r}
render_affiliations(cv_data$distinctions, show_dept = FALSE, hide_end = TRUE)
```

## Publications

### Journal Articles

```{r}
render_publications(journal_articles, highlight_name = "Fabbri")
```

### Articles Under Review

- Distinct tumor microenvironment signatures predict outcomes and correlate
  with PD-L1 in HPV-independent vulvar cancer.
- Cohort Profile Update: The Human Early Life Exposome (HELIX) Cohort.

### Software

```{r}
render_talks(software)
```

**causatr: Causal Effects Estimation** [[link]](https://github.com/etverse/causatr)\
Software | In development

**negatr: Negative Control Analysis** [[link]](https://github.com/etverse/negatr)\
Software | In development

**manuscripts: Scientific Manuscript Template** [[link]](https://github.com/lorenzoFabbri/manuscripts)\
Software | In development

## Talks

See [github.com/lorenzoFabbri/talks](https://github.com/lorenzoFabbri/talks) for slides and materials.

**Transparent causal inference for observational epidemiology**\
Invited talk | Colicino Group, Icahn School of Medicine at Mount Sinai (via Zoom), Jan 2025

## Posters

```{r}
render_talks(posters, number = TRUE)
```

## Continuing Education

```{r}
render_affiliations(cv_data$qualifications)
```

## Service

### Peer Review

- *Scientific Reports* (1 review)

### Working Groups

```{r}
render_affiliations(cv_data$services, show_dept = FALSE)
```

### Memberships

```{r}
render_memberships(cv_data$memberships)
```

## Skills

| Category | Details |
|:---------|:--------|
| Languages | Italian (native), English (C1, IELTS 7.0), Spanish (basic) |
| Programming | R, Python, MATLAB, C |
| Markup | LaTeX, Quarto/RMarkdown |
| Tools | git, SLURM, High Performance Scientific Computing |

::: {.content-visible when-format="html"}
<p class="cv-updated">Last updated: `r format(Sys.Date(), "%B %Y")`</p>
:::
